\LARGE \bf Energy-Aware Dynamic Planning Algorithm for Autonomous UAVs

### 2020-11-30 icra-2021.tex
fixing (need to change the control and the B matrix)

Let us further adopt the following mathematical notation.  $[a]$ is the set $\{0,1,\dots,a\}$, $[a]^+$ the set $[a]/\{0\}$, $\langle a_1,a_2,...,a_n\rangle$ an ordered list of $n$ elements, and $\underline{c},\overline{c}$ the lower and upper bound of the parameter $c$ retrieved from a plan specification. The plan specification is a file which specifies all the stages and triggering points along the plan. We discuss the format in Subsection~\ref{sec:plan}.

@@

  The \emph{plan} is then a function which maps a point to a specific stage $\Gamma_i$. The point $\mathbf{p}_{\Gamma_{i}}$ that allows the transition between $\Gamma_i$ and $\Gamma_{i+1}$ is called \emph{triggering point}.
  \begin{figure}[h]
  \center
  \begin{tikzpicture}[shorten >=1pt,node distance=12ex,on grid,auto] 
    \node        (q_dots0) {$\cdots$};
    \node[state] (q_0) [right=of q_dots0] {$\Gamma_i$};
    \node[state] (q_1) [right=of q_0] {$\Gamma_{i+1}$};
    \node        (q_dots1) [right=of q_1] {$\cdots$};   
    \path[->]
    (q_dots0) edge node{$\mathbf{p}_{\Gamma_{i-1}}$} (q_0)
    (q_0) edge node {$\mathbf{p}_{\Gamma_i}$} (q_1)    
    (q_0) edge [loop above] node {$\mathbf{p}_{k}$} (q_0)
    (q_1) edge node {$\mathbf{p}_{\Gamma_{i+1}}$} (q_dots1)
    (q_1) edge [loop above] node {$\mathbf{p}_{k}$} (q_1)
    ; %end path 
    \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=10pt},yshift=0pt]
    (q_dots0.south west) -- (q_dots1.south east) node [black,midway,yshift=-8ex]{$\Gamma:\mathbb{R}^2\rightarrow\Gamma_i$};
  \end{tikzpicture}
  \caption{Finite state machine of the plan}
  \label{fig:state-machine}
  \end{figure}

@@

  The algorithm takes as input $\Gamma,\bigcup_i{\Gamma_i}$, the triggering points (using the plan specification) and some initial guesses that are necessary for the position and energy estimation. It outputs the new position, the instantaneous energy consumption, and the control input--an action performed evolving the state.
\end{defn}

@@

The next line specifies the triggering point $\mathbf{p}_{\Gamma_1}$
\begin{algorithmic}[1]
  \setcounterref{ALG@line}{code:stage}
  \State\textbf{\texttt{$x$,$y$}}\label{code:trigger-pt}
\end{algorithmic}
where $x$ and $y$ are the two coordinates of the point. The UAV reaches the point within a given radius (a parameter of the algorithm) and enters the next stage $\Gamma_2$.

@@

The state is the UAV's position in space and the energy coefficients in time. We show a linear relation between the instantaneous energy consumption and the energy coefficients in Theorem~\ref{thm:state-vs-energy}, but the two are different. We show after the main results how this approach allows us variability in terms of the systems behaving periodically, piece-wise periodically, or merely linearly with sporadic periodicity.

The set
\begin{equation}\label{eq:area}
  \mathcal{P}_i:=\{\mathbf{p}_k\mid\varphi_i(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho})\in\mathbb{C}_i\},
\end{equation}
delimits the area where the $i$-th TEE $\varphi_i$ is free to evolve using $\rho$ adjustments $\mathbf{c}_i:=c_{i,1},...,c_{i,\rho}$ (the gray area in Figure~\ref{fig:overview}).

The algorithm uses the set from Equation~(\ref{eq:area}) to select the optimal adjustments $\mathbf{c}_i^0$ s.t. $\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$ has the highest instantaneous energy consumption (while still respecting the energy budget). It guides the UAV to the new position $\mathbf{p}_{k+1}$ using the function $\varPhi:=\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$, computing its vector field $\nabla\varPhi:=(\partial\varPhi/\partial x,\partial\varPhi/\partial y)$, and deriving the direction to follow in the form of velocity vector
\begin{equation}\label{eq:pd}
  \dot{\mathbf{p}}_d(\mathbf{p}_k):=E\nabla\varPhi-k_e\varPhi\nabla\varPhi,\,\,\,E=\begin{bmatrix}
    0&1\\-1&0
  \end{bmatrix},
\end{equation}
where $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence. The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading due to the atmospheric interference, such as wind ($w\in\mathbb{R}$ in Figure~\ref{fig:overview}).

>>>>

Let us further adopt the following mathematical notation.  $[a]$ is the set $\{0,1,\dots,a\}$, $[a]^+$ the set $[a]/\{0\}$, $\langle a_1,a_2,...,a_n\rangle$ an ordered list of $n$ elements, $c^0$ the optimal value of parameter $c$,and $\underline{c},\overline{c}$ its lower and upper bound retrieved from a plan specification. The plan specification is a file which specifies all the stages and triggering points along the plan. We discuss the format in Subsection~\ref{sec:plan}. Moreover, we use the notation $c_{i,j}$ to specify the $j$-th item of the $i$-th parameters set $c_i$.

@@

  The \emph{plan} is a finite state machine $\Gamma$ where the state-transition function $\bigcup_i{\Gamma_i}\times\mathbb{R}^2\rightarrow\bigcup_i{\Gamma_i}$ maps a stage and a point to the next stage. The point $\mathbf{p}_{\Gamma_{i}}$ that allows the transition between $\Gamma_i$ and $\Gamma_{i+1}$ is called \emph{triggering point}.

  \begin{figure}[h]
  \center
  \begin{tikzpicture}[shorten >=1pt,node distance=12ex,on grid,auto] 
    \node        (q_dots0) {$\cdots$};
    \node[state] (q_0) [right=of q_dots0] {$\Gamma_i$};
    \node[state] (q_1) [right=of q_0] {$\Gamma_{i+1}$};
    \node        (q_dots1) [right=of q_1] {$\cdots$};   
    \path[->]
    (q_dots0) edge node{$\mathbf{p}_{\Gamma_{i-1}}$} (q_0)
    (q_0) edge node {$\mathbf{p}_{\Gamma_i}$} (q_1)    
    (q_0) edge [loop above] node {$\mathbf{p}_{k}$} (q_0)
    (q_1) edge node {$\mathbf{p}_{\Gamma_{i+1}}$} (q_dots1)
    (q_1) edge [loop above] node {$\mathbf{p}_{k}$} (q_1)
    ; %end path 
    \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=10pt},yshift=0pt]
    (q_dots0.south west) -- (q_dots1.south east) node [black,midway,yshift=-8ex]{$\Gamma$};
  \end{tikzpicture}
  \caption{Finite state machine of the plan}
  \label{fig:state-machine}
  \end{figure}

@@

  The algorithm takes as input the plan, the triggering points (using the plan specification) and some initial guesses that are necessary for the position and energy estimation. It outputs the new position, the instantaneous energy consumption, and the control input--an action performed evolving the state.
\end{defn}

@@

The next line specifies the triggering point $\mathbf{p}_{\Gamma_1}$
\begin{algorithmic}[1]
  \setcounterref{ALG@line}{code:stage}
  \State\textbf{\texttt{$x$,$y$}}\label{code:trigger-pt}
\end{algorithmic}
where $x$ and $y$ are the two coordinates of the point. The UAV reaches the point within a given radius (a parameter of the algorithm) and enters the next stage $\Gamma_2$. The coordinates can be expressed in function of the TEE parameters $c_1$. Generally, one can express the coordinates in function of any TEE parameters $c_i$, propagating the information therein if necessary (see Figure~\ref{fig:state-machine2}).

\begin{figure}[h]
  \center
  \begin{tikzpicture}[shorten >=1pt,node distance=24ex,on grid,auto] 
    \node        (q_dots0) {$\cdots$};
    \node[state] (q_0) [right=of q_dots0] {$\langle\varphi_i,c_i\rangle$};
    \node        (q_dots1) [right=of q_0] {$\cdots$};   
    \path[->]
    (q_dots0) edge node{$\mathbf{p}_{\Gamma_{i-1}}(c_1,\dots,c_{i-1})$} (q_0)
    (q_0) edge node {$\mathbf{p}_{\Gamma_i}(c_1,\dots,c_{i})$} (q_dots1)    
    (q_0) edge [loop above] node {$\mathbf{p}_{k}$} (q_0)
    ; %end path
  \end{tikzpicture}
  \caption{Detail of the stage $\Gamma_i$ in the finite state machine}
  \label{fig:state-machine2}
  \end{figure}

We refer the reader to the example in Appendix~\ref{app:plan-example} for a detailed implementation. In the example, the first TEE parameter is propagated to all the following TEEs and triggering points.

@@

We describe the position with $x,y$ coordinates and the altitude $h$, and the energy with some energy coefficients which describes the energy evolution in time. Here we describe the position evolution using vector field~\cite{de2017guidance}.

Let us assume the set
\begin{equation}\label{eq:area}
  \mathcal{P}_i:=\{\mathbf{p}_k\mid\varphi_i(\mathbf{p}_k,c_{i,1},\dots,c_{i,\rho})\in\mathbb{C}_i\},
\end{equation}
delimits the area where the $i$-th TEE $\varphi_i$ is free to evolve using $\rho$ adjustments $\mathbf{c}_i:=c_{i,1},...,c_{i,\rho}$ (the gray area in Figure~\ref{fig:overview}). Phisically, $\varphi_i$ is function of the two coordinates and is satisfied when a point $\mathbf{p}_k$ is on the TEE. The TEE parameters allows to change the TEE. They are a way to alter the nominal trajectory from the initial plan.

In fact, the algorithm uses the set from Equation~(\ref{eq:area}) to alter the optimal TEE parameters $\mathbf{c}_i^0$ s.t. $\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$ has the highest instantaneous energy consumption (while still respecting the energy budget). It guides the UAV to the new position $\mathbf{p}_{k+1}$ using the function $\varPhi:=\varphi_i(\mathbf{p}_k,\mathbf{c}_i^0)$, computing its vector field $\nabla\varPhi:=(\partial\varPhi/\partial x,\partial\varPhi/\partial y)$, and deriving the direction to follow in the form of velocity vector
\begin{equation}\label{eq:pd}
  \dot{\mathbf{p}}_d(\mathbf{p}_k):=E\nabla\varPhi-k_e\varPhi\nabla\varPhi,\,\,\,E=\begin{bmatrix}
    0&1\\-1&0
  \end{bmatrix},
\end{equation}
where $E$ specifies the rotation (which influence the tracking direction), and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence. The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading due to the atmospheric interference, such as wind ($w\in\mathbb{R}$ in Figure~\ref{fig:overview}).

% fixed up to here!
% idea; write control as parameters; write B as time-dependent, which multiplied TEE parameters gives energy due to trajectory (approx). By computations due to computations (from powprof).
